\vspace{-0.25em}\thetitle

### 2009-07-23 paper.tex
...

The fundamental concept underlying this work is \emph{linear representation of network traffic}~\cite{Karpinski08}.
A linear representation is a function that maps sets of flows to vectors, the coordinates of which describe aspects of flow behavior;
it must distribute additively over set unions.
% the representation must also satisfy a simple linearity condition which we will describe in detail later.
% the sum of the representations of a set of flows is a vector that represents the aggregate behavior of the set of flows.
An entire traffic trace may be represented as a matrix whose rows are the representations of flows in the trace.
We restrict our consideration to a particularly natural and powerful class of representations whose coordinates are the frequencies of flow features in a set of flows.
For example, the representation can have a dimension for each packet size up to 1500; coordinates in these dimensions indicate the number of packets of each size.
Port numbers, \caps{IP} protocol type, and inter-packet intervals can be handled similarly.
% Examples of flow features are the number of packets of a certain size or the use of a particular port number.
% The fundamental premise of this work, and of the sequel, is that the representatives of actual flow behaviors can be understood as being sampled from

@@

A linear representation, as defined by Karpinski~\emph{et~al.}~\cite{Karpinski08}, maps sets of flows into a vector space such that union of sets becomes summation in the vector space:
\begin{align}
  \Phi(s_1 \union s_2) = \Phi(s_1) + \Phi(s_2).
\end{align}
The representation function, $\Phi$, should map each set of flows to a vector which in some sense describes their collective behavior.
For example: let $\Phi(s) \in \R^1$ be the number of packets in all the flows in as set $s$.
Since the number of total packets in the union of two sets of flows is the sum of the number in each individually, this representation is linear.

>>>>

The fundamental concept underlying this work is \emph{linear representation of network traffic}~\cite{Karpinski08}.
A linear representation is a function that maps sets of flows to vectors, the coordinates of which describe aspects of flow behavior;
it must distribute additively over set unions.
% the representation must also satisfy a simple linearity condition which we will describe in detail later.
% the sum of the representations of a set of flows is a vector that represents the aggregate behavior of the set of flows.
An entire traffic trace may be represented as a matrix whose rows are the representations of flows in the trace.
We restrict our consideration to a particularly natural and powerful class of representations whose coordinates are the frequencies of flow features in a set of flows.
For example, the representation can have a dimension for each packet size up to the maximum transfer unit (\caps{MTU});
coordinates in these dimensions indicate the count of packets of each size.
Port numbers, \caps{IP} protocol type, and inter-packet intervals can be handled similarly.
% Examples of flow features are the number of packets of a certain size or the use of a particular port number.
% The fundamental premise of this work, and of the sequel, is that the representatives of actual flow behaviors can be understood as being sampled from

@@

A linear representation, as defined by Karpinski~\emph{et~al.}~\cite{Karpinski08}, maps sets of flows into a vector space such that union of sets becomes summation in the vector space:
\begin{align}
  \Phi(s_1 \union s_2) = \Phi(s_1) + \Phi(s_2).
\end{align}
The representation function, $\Phi$, should map each set of flows to a vector which in some sense describes their collective behavior.
For example: let $\Phi(s) \in \R^1$ be the number of packets in all the flows in the set $s$.
Since the number of total packets in the union of two sets of flows is the sum of the number in each individually, this representation is linear.
Given two representations, their direct sum is readily seen to also be a linear representation:
\begin{align}
  \Phi(s) = \Phi_1(s) \directsum \Phi_2(s).
\end{align}

A particularly powerful class of linear representations describes the behavior of collections of flows using histogram vectors to count the frequencies of various features.
As mentioned before, a 1500-dimensional vector can be used to count the frequency of all possible packets sizes from a single byte up to the typical \caps{MTU} of 1500 bytes.
In this representation, $\Phi(s) \in \R^{1500}$ has as its $i$th entry the number of packets in $s$ of size $i$.
Since \caps{IP} protocol types range from 0 to 255, the frequency of types in a set of flows can be represented in 256 dimensions.
The representation details for port numbers and inter-packet intervals are described detail in \Section{methodology}.
% Source and destination port numbers can similarly be represented using 65536-dimensional vectors.
% For practical purposes, however, this is too large a vector space, so we represent port numbers in 1000-dimensions, and reduce port numbers modulo 1000.
% Finally, we represent inter-packet intervals by first quantizing into 1500 bins of interval values as described by Karpinski~\emph{et~al.} and counting the number of intervals in flows occurring in each bin.
The representation we consider here is a direct sum of such histogram representations.
The combination is a representation in 5256 dimensions.
An entire trace is represented as a matrix of such representation vectors---one flow per row.
This paper explores the linear structure of such matrices.
